Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 approach.tex
moved who comparison to exp section

As a result, a GPU implementation of conjugate gradient converges in 50
ms when using 250 HOG cells, two orders of magnitude faster than the using
Cholesky factorization with Gaussian Elemination. We report the real time
analysis of whitening using decomposition and conjugate gradient methods in
Fig.~\ref{fig:whotime}

@@

\subsection{Variations of WHO}
\label{sec:variations}
To validate our approach, we run an ensemble of NZ-WHO templates as a bank of exemplar detectors and compare its performance with other WHO variants. Since WHO variants uses HOG features, they are slower than HOG templates but WHO variants in general performs better than WHO by significant margin. However, WHO using Cholesky decomposition with Gaussian Elemination takes the most time yet performs worse than NZ-WHO which is two order of magnitude faster to generate.

We also calibrated the various methods

In the experiment, we compared the performance of HOG, WHO, WHO-CG, WHO-CG-Z and NZ-WHO. The WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}

The experiment results is on Tab.~\ref{tab:who_initializations}
We found out that without calibration, NZ-WHO performs the best on object
detection on 3DObject car dataset \cite{Savarese07}. See Table
\ref{tab:who_initializations} for detail. In essence, if we use calibration, we
could achieve better performance but since our goal is to do 2D-3D matching and
continuous viewpoint estimation using on-the-fly template generation, we did not
calibrated our templates.

We empirically found out that NZ-WHO performs reasonably well without time
consuming calibration stage compare to other variational method to generate
templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4
elevations. Each template takes approximately 80 milliseconds to generate a
NZ-WHO template. We also calibrated templates using the method presented in
\cite{Aubry14}. The calibration learns affine transformation of the detection
confidence.% Note that in Section \ref{experiments}, we provide the same
% experiment with 9 CAD models.

\begin{table*}[!htbp]
    \footnotesize
    \begin{center}
\begin{tabular}{|c|c|r|c|r|}
\hline
Methods (AP/MPPE) & before calibration  & time & after calibration \cite{Aubry14} & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.3 / 65.0           &  31ms  & 60.4 / 50.2                 & 8.7 sec \\ 
WHO\cite{Hariharan12} & 82.1 / 85.4           &  3811ms& 84.4 / 83.0                 & 12.4 sec  \\
WHO-CG                & 81.7 / \textbf{84.9}  &  104ms & 83.7 / 87.3                 & 8.3 sec \\
WHO-CG-Z              & 54.4 / 65.1           &  103ms & \textbf{92.8} / 86.7        & 8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG             & \textbf{90.0} / 82.8  &   79ms & 90.3 / \textbf{86.8}        & 8.5 sec   \\
\hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}.}
\label{tab:who_initializations}
\end{table*}

>>>>

As a result, a GPU implementation of conjugate gradient converges in 50
ms when using 250 HOG cells, two orders of magnitude faster than the using
Cholesky factorization with Gaussian Elemination. We report the real time
analysis of whitening using decomposition and conjugate gradient methods in
Fig.~\ref{fig:whotime}.

@@

### 2014-11-14 experiments.tex
moved who comparison to exp section

>>>>

\subsection{Variations of WHO}
\label{sec:variations}
To validate our approach, we run an ensemble of NZ-WHO templates as a bank of exemplar detectors and compare its performance with other WHO variants. Since WHO variants uses HOG features, they are slower than HOG templates but WHO variants in general performs better than WHO by significant margin. However, WHO using Cholesky decomposition with Gaussian Elemination takes the most time yet performs worse than NZ-WHO which is two order of magnitude faster to generate.

We also calibrated the various methods

In the experiment, we compared the performance of HOG, WHO, WHO-CG, WHO-CG-Z and NZ-WHO. The WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}

The experiment results is on Tab.~\ref{tab:who_initializations}
We found out that without calibration, NZ-WHO performs the best on object
detection on 3DObject car dataset \cite{Savarese07}. See Table
\ref{tab:who_initializations} for detail. In essence, if we use calibration, we
could achieve better performance but since our goal is to do 2D-3D matching and
continuous viewpoint estimation using on-the-fly template generation, we did not
calibrated our templates.

We empirically found out that NZ-WHO performs reasonably well without time
consuming calibration stage compare to other variational method to generate
templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4
elevations. Each template takes approximately 80 milliseconds to generate a
NZ-WHO template. We also calibrated templates using the method presented in
\cite{Aubry14}. The calibration learns affine transformation of the detection
confidence.% Note that in Section \ref{experiments}, we provide the same
% experiment with 9 CAD models.

\begin{table*}[!htbp]
    \footnotesize
    \begin{center}
\begin{tabular}{|c|c|r|c|r|}
\hline
Methods (AP/MPPE) & before calibration  & time & after calibration \cite{Aubry14} & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.3 / 65.0           &  31ms  & 60.4 / 50.2                 & 8.7 sec \\ 
WHO\cite{Hariharan12} & 82.1 / 85.4           &  3811ms& 84.4 / 83.0                 & 12.4 sec  \\
WHO-CG                & 81.7 / \textbf{84.9}  &  104ms & 83.7 / 87.3                 & 8.3 sec \\
WHO-CG-Z              & 54.4 / 65.1           &  103ms & \textbf{92.8} / 86.7        & 8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG             & \textbf{90.0} / 82.8  &   79ms & 90.3 / \textbf{86.8}        & 8.5 sec   \\
\hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}.}
\label{tab:who_initializations}
\end{table*}
